### 2016-09-29 results.tex
cheers

Switching now to the case of a \emph{private}~$M$ GBF, we have the following correctness bound.
\todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ GBF. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}

\heading{Privacy. }

\todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same
  attack as correctness, I think?}

>>>>

Finally, we observe that a similar version of the correctness attack
works outside of the ROM, say, when we hash via $H(j,x)=F_K(\langle
j,x \rangle)$ and assume~$F_K$ is a secure PRF.  Here, $\privaux=K$.  Now,
however, the work switches from offline hash evaluations (i.e., random
oracle calls) to online set-membership (i.e., $\TestOracle$) queries.

Switching now to the case of a \emph{private}~$M$ GBF, we have the
following correctness bound.

\todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ GBF. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}

\heading{Privacy. }
We observe i
\todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same
  attack as correctness, I think?}
